Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2022-03-24 ms.tex
Adding a rough introduction of the time-dependent motivation, including references to Roy et al 2010 and Xu et al 2011

>>>>

\textbf{NOT SURE WHERE TO PUT THIS: Steady-state solutions to this problem, while informative, are not always sufficient to describe all the physics of \lya transport. Time-variable, optically-thick environments necessitate a time-dependent solution to include the dynamic effects of \lya transfer. For example, \lya radiation pressure is dynamically significant in the case of CR7, a \lya emitter in which radiation-driven winds and line cooling play an important role \citep{2017A&G....58c3.22S}. Other time-dependent \lya sources include the optical afterglow of gamma-ray bursts \citep{2010ApJ...716..604R} and sources redshifted by cosmological expansion, which may reveal information about their neutral hydrogen halos and the intergalactic medium \citep{2011MNRAS.418..853X}.}
